```{r}
library(ggplot2)
library(tibble)
```

```{r}
mpg |>
  ggplot(aes(displ, hwy, colour = drv)) + 
  geom_point()
```

```{r}
mpg |>
  ggplot(aes(displ, hwy, colour = drv, size = cyl)) + 
  geom_point(show.legend = FALSE) + 
  theme_void() + 
  scale_color_brewer()
```

```{r}
mpg |>
  ggplot(aes(displ, hwy, colour = drv)) + 
  geom_point(show.legend = FALSE, size = 4) + 
  geom_point(show.legend = FALSE, size = 1, colour = "#222222") + 
  coord_polar() + 
  theme_void() + 
  scale_color_brewer()
```

```{r}
set.seed(1)
n <- 50
dat <- tibble(
  x0 = runif(n),
  y0 = runif(n),
  x1 = x0 + runif(n, min = -.2, max = .2),
  y1 = y0 + runif(n, min = -.2, max = .2),
  shade = runif(n), 
  size = runif(n)
)
dat
```

```{r}
dat |> 
  ggplot(aes(
    x = x0,
    y = y0,
    xend = x1,
    yend = y1,
    colour = shade,
    linewidth = size
  )) +
  geom_segment(show.legend = FALSE) +
  coord_polar() +
  scale_y_continuous(expand = c(0, 0)) +
  scale_x_continuous(expand = c(0, 0)) + 
  scale_color_viridis_c() + 
  scale_size(range = c(0, 10)) + 
  theme_void()
```

```{r}
 create_art <- function(num_circles = 20, num_lines = 20, circle_col = "blue", circle_border = "white", circle_shape = 21, circle_size = 3, line_col = "red", line_size = 1, background_col = "black", seed = 1) {

  # Set seed for reproducibility
  set.seed(seed)
  
  # Generate random data for circles
  circles <- data.frame(
    x = runif(num_circles),
    y = runif(num_circles),
    r = runif(num_circles, 0.01, 0.05)
  )
  
  # Generate random data for lines
  lines <- data.frame(
    x1 = runif(num_lines),
    y1 = runif(num_lines),
    x2 = runif(num_lines),
    y2 = runif(num_lines)
  )
  
  # Create the plot
  p <- ggplot() +
    # Add circles
    geom_point(data = circles, aes(x = x, y = y), shape = circle_shape, size = circle_size, fill = circle_col, color = circle_border, alpha = 0.7) +
    # Add lines
    geom_segment(data = lines, aes(x = x1, y = y1, xend = x2, yend = y2), color = line_col, size = line_size, alpha = 0.7) +
    # Customize the theme
    theme_void() +
    theme(
      panel.background = element_rect(fill = background_col, color = background_col)
    )
  
  # Display the plot
  return(p)
  
}
```

```{r}
create_art(num_circles = 100, num_lines = 100, circle_col = "orange", circle_border = "orange", circle_shape = 21, circle_size = 3, line_col = "yellow", line_size = 1, background_col = "skyblue", seed = 1)

create_art(num_circles = 50, num_lines = 40, circle_col = "orange", circle_border = "orange", circle_shape = 21, circle_size = 7, line_col = "yellow", line_size = 1, background_col = "skyblue", seed = 1)

create_art(num_circles = 80, num_lines = 50, circle_col = "orange", circle_border = "orange", circle_shape = 21, circle_size = 3, line_col = "yellow", line_size = 1, background_col = "skyblue", seed = 7)
```

```{r}
create_art(num_circles = 80, num_lines = 50, circle_col = "purple", circle_border = "purple", circle_shape = 21, circle_size = 5, line_col = "green", line_size = 1, background_col = "black", seed = 7)
```

Title: Lazer Tag

Description: This art piece by astute artist, Ryan DeStefano, aims to reflect the childlike mind when thinking about a simple fun activity such as lazer tag. In this top down view of a lazer tag arena, the purple dots represent participants while the lime green lines represent the lazers being shot.

Code Choices:

-   By setting the num_circles arg to 80, we obtain 80 dots in the image.

-   By setting num_lines to 50, we obtain 50 lines in the image.

-   By setting circle_col to "purple", the dots are filled in with purple.

-   By setting circle_border to "purple", the border of the dots are purple.

-   By setting circle_shape to 21, we get circles for the shape of the points.

-   By setting circle_size to 5, the size of the points is decided, in this case they are relatively large.

-   By setting line_col to "green", the lines become green.

-   The line size is set by specifying the arg line_size.

-   The background of the image is set to black with the background_col arg.

-   The seed arg is set to 7, I just like that number, it could be anything.
